---
title: "Project Code"
author: "Isabel Xiao"
date: "2024-11-26"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data Cleaning

```{r}
# Loading in data & packages
library(tidyverse)
library(tidygeocoder)
library(ggplot2)
library(ggthemes)
library(ggalluvial)
library(plotly)
library(treemapify)
library(fmsb)
library(viridis)
library(bslib)
library(shiny)
library(RColorBrewer)
uva_housing = read.csv("uva_housing_FINAL.csv")


# Add a column of management property or individual landlord


uva_housing <- uva_housing %>%
  mutate(
    Ownership = case_when(
      Management_Company %in% c("MSC", "Real Property Management", "Woodard Properties", "Inv Group LLC", "Arlington Park Townhomes", "Atrium", "Breeden Property Management", "CBS", "Cathcart Property Management", "Dominion Realty Partners", "Godfrey Property Management", "Fogelman Properties", "Frye Properties", "Metzger & Company Inc", "NewCastle Management", "RPM", "Royal Blue Properties", "Shamrock Corporation", "Thalhimer Multifamily", "The New House Company", "The Scion Group", "University Apartments LLC", "University Partners", "Vest Residential") ~ "Company",
      TRUE ~ "Landlord"
    )
  )



# Add a column of rent by bedroom, deal with the ranges
uva_housing2 = uva_housing
uva_housing2 <- uva_housing %>%
  mutate(Total_Price = gsub("\\$|\\s", "", Total_Price)) %>%
  mutate(Total_Price = gsub("\\,|\\s", "", Total_Price)) %>% 
  separate(Num_Bedrooms, into = c("Bedrooms_Low", "Bedrooms_High"), sep = "-", fill = "right", convert = TRUE) %>%
  separate(Num_Bathrooms, into = c("Bathrooms_Low", "Bathrooms_High"), sep = "-", fill = "right", convert = TRUE) %>%
  separate(Total_Price, into = c("Price_Low", "Price_High"), sep = "-", fill = "right", convert = TRUE) %>%
  mutate(
    Bedrooms_High = ifelse(is.na(Bedrooms_High), Bedrooms_Low, Bedrooms_High),
    Bathrooms_High = ifelse(is.na(Bathrooms_High), Bathrooms_Low, Bathrooms_High),
    Price_High = ifelse(is.na(Price_High), Price_Low, Price_High)
    ) %>%
  rowwise() %>%
  do(data.frame(
    Name = .$Name,
    Address = .$Address,
    Housing_Type = .$Housing_Type,
    Neighborhood = .$Neighborhood,
    Distance_UVA = .$Distance_UVA,
    Sq_Feet = .$Sq_Feet,
    Ownership = .$Ownership,
    Management_Company = .$Management_Company,
    Num_Bedrooms = c(.$Bedrooms_Low, .$Bedrooms_High),
    Num_Bathrooms = c(.$Bathrooms_Low, .$Bathrooms_High),
    Total_Price = c(.$Price_Low, .$Price_High)
    )) %>%
  ungroup() %>% 
  mutate(Price_Per_Bedroom = as.numeric(Total_Price) / as.numeric(Num_Bedrooms))

# Delete duplicate rows
uva_housing = uva_housing %>% distinct(Name, .keep_all = TRUE)
uva_housing2 <- uva_housing2[!duplicated(uva_housing2), ]




write.csv(uva_housing2, "uva_housing2.csv")


# Okay other stuff
uva_housing2 = read.csv("uva_housing2.csv")

uva_housing2$Price_Per_Bedroom = as.numeric(uva_housing2$Price_Per_Bedroom)
uva_housing2$Total_Price = as.numeric(uva_housing2$Total_Price)

uva_housing2 = uva_housing2 %>% mutate(Listing_ID = row_number())
```

## Scatterplot of Price per Bedroom vs Distance from UVA

```{r, fig.show="hide"}
# Remove outlier
uva_housing_plot3 = uva_housing2 %>% filter(Distance_UVA <= 20)

uva_housing_plot3$Neighborhood <- factor(
  uva_housing_plot3$Neighborhood,
  levels = c("JPA", "Corner", "Lewis Mountain", "Barracks", "Starr Hill", "Venable", "10th St", "Eagles Landing", "Downtown", "North Downtown", "Other/Far") # Replace with your specific order
)

# Make scatterplot
scatterplot = plot_ly(uva_housing_plot3, x=~Distance_UVA, y=~Price_Per_Bedroom, color=~Neighborhood, type='scatter', mode='markers', colors ='plasma', frame = ~Neighborhood)

scatterplot %>% layout(
  title = 'Price per Bedroom vs Distance from UVA',
  xaxis = list(title = 'Distance from UVA', gridcolor = "gray", zerolinecolor = "gray"),
  yaxis = list(title = 'Price Per Bedroom',  gridcolor = "gray"),
  plot_bgcolor = "black",
  paper_bgcolor = "black",
  font = list(
      family = "Arial, sans-serif",
      size = 12,
      color = "white"
  ),
  showlegend = FALSE,
  updatemenus = list(
    list(
        x = 0, # Adjust x position (0 to 1, left to right)
        y = 1
      )
  )
)
```

```{r, fig.show="hide"}
uva_housing_plot3 = uva_housing2 %>% filter(Neighborhood != "Other/Far")

scatterplot = plot_ly(uva_housing_plot3, x=~Distance_UVA, y=~Price_Per_Bedroom, color=~Neighborhood, type='scatter', mode='markers', colors ='plasma') 

scatterplot %>% layout(
  title = 'Price per Bedroom vs Distance from UVA',
  xaxis = list(title = 'Distance from UVA', gridcolor = "gray", zerolinecolor = "gray"),
  yaxis = list(title = 'Price Per Bedroom', gridcolor = "gray"),
  plot_bgcolor = "black",
  paper_bgcolor = "black",
  font = list(
      family = "Arial, sans-serif",
      size = 12,
      color = "white"
  )
) 
```

## Bar graph with available rentals by neighborhood

```{r, fig.show="hide"}
ggplot(uva_housing, aes(x=Neighborhood, fill=Neighborhood)) + 
  geom_bar(stat="count") +
  labs(x="Neighborhood", y="Count", title="Count of UVA Off-Grounds Housing Neighborhoods") +
  theme(axis.text.x = element_text(angle = 20, color = "white"),
        axis.text.y = element_text(color = "white"), 
        axis.title = element_text(color = "white"), 
        plot.title = element_text(hjust = 0.5, color = "white"), 
        panel.grid.major.x = element_line(color="#242323"),
        panel.grid.major.y = element_line(color="#242323"),
        panel.grid.minor.x = element_line(color="#242323"),
        panel.grid.minor.y = element_line(color="#242323"),
        panel.background = element_rect(fill = "black"),
        plot.background = element_rect(fill = "black"),
        legend.background = element_rect(fill = "black"), 
        legend.text = element_text(color = "white"), 
        legend.title = element_text(color = "white"),
        legend.position = "none") +
  scale_fill_viridis_d(option="plasma")
```

## Boxplots with average distribution by neighborhood

```{r, fig.show="hide"}
ggplot(uva_housing2, aes(x=Price_Per_Bedroom, y=Neighborhood, fill=Neighborhood)) +
  geom_boxplot(color="white") +
  labs(x="Rent Price Per Bedroom", y="Neighborhood", title="Rent Price Distribution by Neighborhood") +
  scale_fill_viridis_d(option="plasma") +
  theme(axis.text.x = element_text(color = "white"),
        axis.text.y = element_text(color = "white"), 
        axis.title = element_text(color = "white"), 
        plot.title = element_text(hjust = 0.5, color = "white"), 
        panel.grid.major.x = element_line(color="#242323"),
        panel.grid.major.y = element_line(color="#242323"),
        panel.grid.minor.x = element_line(color="#242323"),
        panel.grid.minor.y = element_line(color="#242323"),
        panel.background = element_rect(fill = "black"),
        plot.background = element_rect(fill = "black"),
        legend.background = element_rect(fill = "black"), 
        legend.text = element_text(color = "white"), 
        legend.title = element_text(color = "white"),
        legend.position = "none")
```

## Bar graph with top 6 management companies 

```{r, fig.show="hide"}
uva_housing %>% group_by(Management_Company) %>% summarise(count=n()) %>% arrange(., -count)

uva_housing <- uva_housing %>%
  mutate(
    Relevant_Management = case_when(
      Management_Company %in% c("Real Property Management", "Woodard Properties", "MSC", "Inv Group LLC", "CBS", "Godfrey Property Management") ~ Management_Company,
      TRUE ~ "Other"
    )
  )

uva_housing <- uva_housing %>%
  mutate(
    Top6 = case_when(
      Management_Company %in% c("Real Property Management", "Woodard Properties", "MSC", "Inv Group LLC", "CBS", "Godfrey Property Management") ~ "Top 6",
      TRUE ~ "Other"
    )
  )

ggplot(uva_housing, aes(y=Top6, fill=Relevant_Management)) + 
  geom_bar(stat="count") +
  labs(y="Management", x="Count", title="Count of Top 6 Management Companies") +
  scale_fill_viridis_d(option="plasma", name="Top 6 Management") +
  theme(axis.text.x = element_text(color = "white"),
        axis.text.y = element_text(color = "white"), 
        axis.title = element_text(color = "white"), 
        plot.title = element_text(hjust = 0.5, color = "white"), 
        panel.grid.major.x = element_line(color="#242323"),
        panel.grid.major.y = element_line(color="#242323"),
        panel.grid.minor.x = element_line(color="#242323"),
        panel.grid.minor.y = element_line(color="#242323"),
        panel.background = element_rect(fill = "black"),
        plot.background = element_rect(fill = "black"),
        legend.background = element_rect(fill = "black"), 
        legend.text = element_text(color = "white"), 
        legend.title = element_text(color = "white"))

# Introduce breaks
```

## Alluvial plot with management and housing type

```{r, fig.show="hide"}

uva_housing2 <- uva_housing2 %>%
  mutate(Housing_Abbreviation = case_when(
    Housing_Type == "Apartment Complex" ~ "AC",
    Housing_Type == "House" ~ "H",
    Housing_Type == "Townhouse" ~ "T",
    Housing_Type == "Apartment in House" ~ "AH",
    TRUE ~ "Other"  # In case there are other values, we use "Other" as a default
  ))

bright_colors <- c("#F0F921FF", "#FCA636FF", "#E16462FF", "#6A00A8FF")  # Bright colors from the plasma palette

ggplot(uva_housing2, aes(axis1 = Ownership, axis2 = Housing_Type)) +
  geom_alluvium(aes(fill=factor(Housing_Type)),
                width = 0, reverse=FALSE, alpha=0.8) +
  guides(fill='none') +
  geom_stratum(width=1/8, reverse=FALSE, color="#242323") +
  geom_text(color="black", stat = "stratum", aes(label= after_stat(stratum)), reverse = FALSE, angle=20, size=3) +
  scale_x_continuous(breaks = 1:3, labels = c("Ownership", "Housing Type", "Number of Bedrooms")) +
  ggtitle("Alluvial Plot of Housing Types by Ownership") +
  scale_fill_manual(values=bright_colors) + # Use plasma color palette
  theme(
    axis.text.x = element_text(color = "white"),
    axis.text.y = element_text(color = "white"), 
    axis.title = element_text(color = "white"), 
    plot.title = element_text(hjust = 0.5, color = "white"), 
    panel.grid.major.x = element_line(color = "#242323"),
    panel.grid.major.y = element_line(color = "#242323"),
    panel.grid.minor.x = element_line(color = "#242323"),
    panel.grid.minor.y = element_line(color = "#242323"),
    panel.background = element_rect(fill = "black"),
    plot.background = element_rect(fill = "black"),
    legend.background = element_rect(fill = "black"), 
    legend.text = element_text(color = "white"), 
    legend.title = element_text(color = "white")
  )

```

## 7: Are prices different across types of housing?

```{r, fig.show="hide"}
uva_housing2 <- uva_housing2 %>%
  mutate(Housing_Type = case_when(
    Housing_Type == "AC" ~ "Apartment Complex",
    Housing_Type == "T"  ~ "Townhouse",
    Housing_Type == "AH" ~ "Apartment in House",
    Housing_Type == "H"  ~ "House",
    TRUE ~ Housing_Type # Keeps original value if not matched
  ))

bright_colors <- c("#FCA636FF", "#B12A90FF", "#6A00A8FF", "#0D0887FF")

ggplot(uva_housing2, aes(factor(Housing_Type), Price_Per_Bedroom, fill=Housing_Type)) + geom_violin(alpha=0.8) + geom_jitter(color="white", width = 0.1, alpha=0.4, size=1.8) +
  labs(x="Housing Type", y="Price Per Bedroom", title="Rent Price Distribution by Housing Type", fill="Housing Type") +
  theme(axis.text.x = element_text(color = "white"),
    axis.text.y = element_text(color = "white"), 
    axis.title = element_text(color = "white"), 
    plot.title = element_text(hjust = 0.5, color = "white"), 
    panel.grid.major.x = element_line(color = "#242323"),
    panel.grid.major.y = element_line(color = "#242323"),
    panel.grid.minor.x = element_line(color = "#242323"),
    panel.grid.minor.y = element_line(color = "#242323"),
    panel.background = element_rect(fill = "black"),
    plot.background = element_rect(fill = "black"),
    legend.background = element_rect(fill = "black"), 
    legend.text = element_text(color = "white"), 
    legend.title = element_text(color = "white"),
    legend.position = "none") +
  scale_fill_manual(values=bright_colors)
```



## 8: What are the characteristics of listings above $1000 per bedroom?

```{r, fig.show="hide"}
uva_housing2 = uva_housing2 %>% rename(Management = Management_Company)

ui <- fluidPage(
      #"Graphs",
      sidebarLayout(
        sidebarPanel(
          sliderInput("minPrice", "Minimum Price", min = 500, max=2400, value=1000, step=100),
          HTML("<p style='font-size: 14px;'>Move the slider to display characteristics of listings above this minimum rent price.</p>")
        ),
      mainPanel(
        plotOutput("companiesPlot"),
        plotOutput("neighborhoodPlot"),
        plotOutput("housingTypePlot")
    )
  )
)

server <- function(input, output) {
  output$companiesPlot <- renderPlot({
    filtered_data <- uva_housing2 %>% filter(Price_Per_Bedroom >= input$minPrice)
    
    data_summary <- filtered_data %>%
      group_by(Management) %>%
      summarise(Count = n())
    
    bright_colors <- c("#0D0887FF", "#B12A90FF", "#56106EFF", "#FCA636FF", "#6A00A8FF")
    continuous_palette <- colorRampPalette(bright_colors)
    
    unique_management <- unique(data_summary$Management)  # Get unique categories
    random_colors <- sample(bright_colors, length(unique_management), replace=TRUE)  # Sample colors

    # Map the random colors to each Management category
    color_mapping <- setNames(random_colors, unique_management)
    
    # Treemap
    ggplot(data_summary, aes(area = Count, fill = Management, label = Management)) +
      geom_treemap() +
      geom_treemap_text(colour = "white", place = "centre", grow = TRUE) +
      labs(title = "Management of Listings Above Minimum Price") +
      theme(axis.text.x = element_text(angle = 20, color = "white"),
        axis.text.y = element_text(color = "white"), 
        axis.title = element_text(color = "white"), 
        plot.title = element_text(hjust = 0.5, color = "white"), 
        panel.grid.major.x = element_line(color="#242323"),
        panel.grid.major.y = element_line(color="#242323"),
        panel.grid.minor.x = element_line(color="#242323"),
        panel.grid.minor.y = element_line(color="#242323"),
        panel.background = element_rect(fill = "black"),
        plot.background = element_rect(fill = "black"),
        legend.background = element_rect(fill = "black"), 
        legend.text = element_text(color = "white"), 
        legend.title = element_text(color = "white"),
        legend.position = "none") +
      scale_fill_manual(values=color_mapping) +  # Repeating Stata colors
      guides(fill = "none")
  })
  
  output$neighborhoodPlot <- renderPlot({
    filtered_data <- uva_housing2 %>% filter(Price_Per_Bedroom >= input$minPrice)
    
    overall_avg_price <- mean(filtered_data$Price_Per_Bedroom)
    
    ggplot(filtered_data, aes(x = Neighborhood, y = Price_Per_Bedroom, color = Neighborhood)) +
       geom_hline(yintercept = overall_avg_price, linetype = "dashed", color = "#F0F921FF", size = 1) +  # Horizontal average line
       geom_segment(aes(x = Neighborhood, 
                        xend = Neighborhood, 
                        y = overall_avg_price, 
                        yend = Price_Per_Bedroom),
                    color = "white", 
                    size = 0.8) +  # Lollipop stem
       geom_point(size = 5) +  # Lollipop head
       labs(
         title = paste("Prices by Neighborhood with Average Price Line of: ", round(overall_avg_price, 2)),
         x = "Neighborhood",
         y = "Price Per Bedroom"
       ) +
       theme(
         axis.text.x = element_text(color = "white"),
        axis.text.y = element_text(color = "white"), 
        axis.title = element_text(color = "white"), 
        plot.title = element_text(hjust = 0.5, color = "white"), 
        panel.grid.major.x = element_line(color="#242323"),
        panel.grid.major.y = element_line(color="#242323"),
        panel.grid.minor.x = element_line(color="#242323"),
        panel.grid.minor.y = element_line(color="#242323"),
        panel.background = element_rect(fill = "black"),
        plot.background = element_rect(fill = "black"),
        legend.background = element_rect(fill = "black"), 
        legend.text = element_text(color = "white"), 
        legend.title = element_text(color = "white"),
        legend.position = "none"
       ) + scale_color_viridis_d(option="plasma") 
  
})
  
  output$housingTypePlot <- renderPlot({
    filtered_data <- uva_housing2 %>% filter(Price_Per_Bedroom >= input$minPrice)
    
    # Bar Graph
    ggplot(filtered_data, aes(x=Housing_Type, fill=Housing_Type)) +
      geom_bar(stat="count") +
      labs(x="Housing Type", y="Count", title="Housing Type of Listings Above Minimum Price") +
      theme(axis.text.x = element_text(color = "white"),
        axis.text.y = element_text(color = "white"), 
        axis.title = element_text(color = "white"), 
        plot.title = element_text(hjust = 0.5, color = "white"), 
        panel.grid.major.x = element_line(color="#242323"),
        panel.grid.major.y = element_line(color="#242323"),
        panel.grid.minor.x = element_line(color="#242323"),
        panel.grid.minor.y = element_line(color="#242323"),
        panel.background = element_rect(fill = "black"),
        plot.background = element_rect(fill = "black"),
        legend.background = element_rect(fill = "black"), 
        legend.text = element_text(color = "white"), 
        legend.title = element_text(color = "white"),
        legend.position = "none") +
      scale_fill_viridis_d(option="plasma")
  })
  
}
shinyApp(ui = ui, server = server)
```


## 9: Comparing Listings with Lollipop Plots

```{r, fig.show="hide"}
uva_housing2 <- uva_housing2 %>%
  mutate(Listing_ID = row_number())

uva_housing2 <- uva_housing2 %>%
  mutate(Listing_ID2 = paste("Listing_ID: ", row_number()))

ui <- fluidPage(
  
  navset_card_underline(
    nav_panel("Listing Comparison Table",
              sidebarLayout(
                sidebarPanel(
                  numericInput("priceHigh", "High end price/bedroom", 800, min = 0),
                  numericInput("priceLow", "Low end price/bedroom", 400, min = 0),
                  selectInput("neighborhood", "Select Neighborhood", 
                              choices = c("All", unique(uva_housing2$Neighborhood)), 
                              multiple = FALSE),
                  sliderInput("distance_uva", "Distance from UVA (miles)", min = 0, max = 10, step = 0.1, value = 0.1),
                  sliderInput("num_bedrooms", "Number of bedrooms", min = 1, max = 4, value = 2),
                  selectInput("housing_type", "Select Housing Type", 
                              choices = c("All", unique(uva_housing2$Housing_Type)), 
                              multiple = FALSE)
                ),
                mainPanel(
                  tableOutput("ListingSelector")
                )
              )
              
    ),
    nav_panel("Top 3 Listing Comparison",
              sidebarLayout(
                sidebarPanel(
                  numericInput("pricePreferred", "Preferred Price", 800, min = 0),
                  numericInput("priceRange", "Price Range (preferred price plus/minus)", 200, min = 0),
                  selectInput("neighborhood", "Select Neighborhood", 
                              choices = c("All", unique(uva_housing2$Neighborhood)), 
                              multiple = FALSE),
                  sliderInput("distance_uva", "Distance from UVA (miles)", min = 0, max = 10, step = 0.1, value = 1),
                  sliderInput("num_bedrooms", "Number of bedrooms", min = 1, max = 4, value = 2),
                  sliderInput("num_bathrooms", "Number of bathrooms", min = 1, max = 4, value = 2),
                  selectInput("housing_type", "Select Housing Type", 
                              choices = c("All", unique(uva_housing2$Housing_Type)), 
                              multiple = FALSE),
                ),
                mainPanel(
                  uiOutput("checkboxUI"),
                  plotOutput("bedroomPlot"),
                  plotOutput("bathroomPlot"),
                  plotOutput("distancePlot"),
                  plotOutput("pricePlot")
                  
                )
              )
    )
  )
)

server <- function(input, output, session) {
  output$ListingSelector <- renderTable({
    uva_housing2 %>% 
      filter(Price_Per_Bedroom <= input$priceHigh,
             Price_Per_Bedroom >= input$priceLow,
             Num_Bedrooms == input$num_bedrooms,
             (Neighborhood == input$neighborhood | input$neighborhood == "All"),
             (Housing_Type == input$housing_type | input$housing_type == "All"),
             Distance_UVA <= input$distance_uva)
  })
  
  
  # Reactive filtered data based on user preferences
  filtered_data <- reactive({
    uva_housing2 %>%
      filter(Price_Per_Bedroom <= input$pricePreferred + input$priceRange,
             Price_Per_Bedroom >= input$pricePreferred - input$priceRange,
             Num_Bedrooms <= input$num_bedrooms,
             (Neighborhood == input$neighborhood | input$neighborhood == "All"),
             (Housing_Type == input$housing_type | input$housing_type == "All"),
             Distance_UVA <= input$distance_uva)
  })
  
  # Generate checkboxes for filtered listings
  output$checkboxUI <- renderUI({
    available_listings <- filtered_data()
    checkboxGroupInput(
      "selected_listings",
      label = NULL,
      choices = setNames(available_listings$Listing_ID, 
                         paste("Name: ", available_listings$Name, " Price:", available_listings$Price_Per_Bedroom,
                               "Beds:", available_listings$Num_Bedrooms,
                               "Bathrooms:", available_listings$Num_Bathrooms,
                               "Dist:", round(available_listings$Distance_UVA, 2), "mi")),
      selected = NULL
    )
  })
  
  # Observe the selected listings to enforce a maximum of 5 selections
  observeEvent(input$selected_listings, {
    if (length(input$selected_listings) > 5) {
      # Remove the last selected item if more than 5 are selected
      updateCheckboxGroupInput(
        session, "selected_listings",
        selected = head(input$selected_listings, 5)
      )
      showNotification("You can only select up to 3 listings.", type = "warning")
    }
  })
  
  
  # Lollipop plot function

  plot_variable <- function(data, x_var, preferred_value, title) {
    ggplot(data, aes_string(y = "Listing_ID2", x = x_var)) +
      geom_segment(aes_string(xend = x_var, yend = "Listing_ID2"), color = "black") +
      geom_vline(xintercept = preferred_value, linetype = "dashed", color = "#F0F921FF", linewidth = 1) +
      geom_point(size = 8, color = "#6A00A8FF") +
      geom_text(aes_string(label = x_var), vjust = -0.5, color = "white") +
      geom_segment(aes(x = preferred_value, xend = !!sym(x_var), y = Listing_ID2, yend = Listing_ID2), 
                   color = "#FCA636FF", linetype = "dotted", linewidth = 1) + 
      scale_x_continuous(limits = c(preferred_value - 2, preferred_value + 2)) +  # Center on preferred value
      theme(axis.text.x = element_text(color = "white"),
            axis.text.y = element_text(color = "white"), 
            axis.title = element_text(color = "white"), 
            plot.title = element_text(hjust = 0.5, color = "white"), 
            panel.grid.major.x = element_line(color="#242323"),
            panel.grid.major.y = element_line(color="#242323"),
            panel.grid.minor.x = element_line(color="#242323"),
            panel.grid.minor.y = element_line(color="#242323"),
            panel.background = element_rect(fill = "black"),
            plot.background = element_rect(fill = "black"),
            legend.background = element_rect(fill = "black"), 
            legend.text = element_text(color = "white"), 
            legend.title = element_text(color = "white"),
            legend.position = "none") +
      labs(title = title, x = title, y = NULL)
  }
  
  # Lollipop plots
  output$bedroomPlot <- renderPlot({
    selected_listings <- filtered_data() %>% 
      filter(Listing_ID %in% input$selected_listings)
    plot_variable(selected_listings, "Num_Bedrooms", input$num_bedrooms, "Number of Bedrooms")
  })
  
  output$bathroomPlot <- renderPlot({
    selected_listings <- filtered_data() %>% 
      filter(Listing_ID %in% input$selected_listings)
    plot_variable(selected_listings, "Num_Bathrooms", input$num_bathrooms, "Number of Bathrooms")
  })
  
  output$distancePlot <- renderPlot({
    selected_listings <- filtered_data() %>% 
      filter(Listing_ID %in% input$selected_listings)
    plot_variable(selected_listings, "Distance_UVA", input$distance_uva, "Distance from UVA (miles)")
  })
  
  output$pricePlot <- renderPlot({
    selected_listings <- filtered_data() %>% 
      filter(Listing_ID %in% input$selected_listings)
    
    
    # Set x-axis range based on input price range
    price_min <- input$pricePreferred - input$priceRange
    price_max <- input$pricePreferred + input$priceRange
    
    # Generate plot
    ggplot(selected_listings, aes_string(y = "Listing_ID2", x = "Price_Per_Bedroom")) +
      geom_segment(aes_string(xend = "Price_Per_Bedroom", yend = "Listing_ID2"), color = "black") +
      geom_vline(xintercept = input$pricePreferred, linetype = "dashed", color = "#F0F921FF", linewidth = 1) +  # Red dashed line at preferred price
      geom_point(size = 8, color = "#6A00A8FF") +
      geom_text(aes_string(label = "Price_Per_Bedroom"), vjust = -0.5, color = "white") +
      geom_segment(aes(x = Price_Per_Bedroom, xend = input$pricePreferred, y = Listing_ID2, yend = Listing_ID2), 
                   color = "#FCA636FF", linetype = "dotted", linewidth = 1) + 
      scale_x_continuous(limits = c(price_min, price_max)) +  # X-axis interval from preferred - range to preferred + range
      theme(axis.text.x = element_text(color = "white"),
            axis.text.y = element_text(color = "white"), 
            axis.title = element_text(color = "white"), 
            plot.title = element_text(hjust = 0.5, color = "white"), 
            panel.grid.major.x = element_line(color="#242323"),
            panel.grid.major.y = element_line(color="#242323"),
            panel.grid.minor.x = element_line(color="#242323"),
            panel.grid.minor.y = element_line(color="#242323"),
            panel.background = element_rect(fill = "black"),
            plot.background = element_rect(fill = "black"),
            legend.background = element_rect(fill = "black"), 
            legend.text = element_text(color = "white"), 
            legend.title = element_text(color = "white"),
            legend.position = "none") +
      labs(title = "Price Per Bedroom", x = "Price Per Bedroom", y = NULL)
  })
}

shinyApp(ui = ui, server = server)

```
